Towards Reliable Machine Learning Deployments in the Cloud

### 2024-03-28 plots/cifar/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -550 & 0.856 & -550 & 0.266 & 0.219 \\
cox & -- & 0.856 & -- & 0.202 & 0.254 \\
log_logistic & -562 & 0.857 & -562 & 0.258 & 0.215 \\
log_normal & -568 & 0.857 & -568 & 0.258 & 0.216 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrrlrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
weibull & -1292.89 & 0.79 & 0.80 & -1292.89 & 0.20 & 0.67 \\
cox & -- & 0.80 & 0.80 & -- & 0.12 & 0.11 \\
log_logistic & -1474.32 & 0.79 & 0.79 & -1474.32 & 0.17 & 0.20 \\
log_normal & -1459.29 & 0.79 & 0.79 & -1459.29 & 0.18 & 0.21 \\
\bottomrule
\end{tabular}
\end{table}

### 2024-03-28 plots/cifar100/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -361 & 0.845 & -361 & 0.331 & 0.179 \\
cox & -- & 0.847 & -- & 0.238 & 0.162 \\
log_logistic & -371 & 0.852 & -371 & 0.318 & 0.172 \\
log_normal & -372 & 0.851 & -372 & 0.313 & 0.174 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrrlrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
weibull & -1159.72 & 0.79 & 0.76 & -1159.72 & 0.21 & 0.21 \\
cox & -- & 0.79 & 0.76 & -- & 0.13 & 0.13 \\
log_logistic & -1313.15 & 0.78 & 0.77 & -1313.15 & 0.20 & 0.20 \\
log_normal & -1299.38 & 0.79 & 0.77 & -1299.38 & 0.20 & 0.20 \\
\bottomrule
\end{tabular}
\end{table}

### 2024-03-28 plots/mnist/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -778 & 0.886 & -778 & 0.238 & 0.204 \\
cox & -- & 0.888 & -- & 0.185 & 0.201 \\
log_logistic & -759 & 0.884 & -759 & 0.226 & 0.204 \\
log_normal & -752 & 0.881 & -752 & 0.225 & 0.202 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrrlrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
weibull & -1631.26 & 0.90 & 0.89 & -1631.26 & 0.15 & 0.69 \\
cox & -- & 0.90 & 0.89 & -- & 0.11 & 0.11 \\
log_logistic & -1842.71 & 0.90 & 0.90 & -1842.71 & 0.14 & 0.19 \\
log_normal & -1799.93 & 0.90 & 0.90 & -1799.93 & 0.14 & 0.29 \\
\bottomrule
\end{tabular}
\end{table}
